---
title: "Abigail Balint - DACSS 690V Final Dashboard"
bibliography: AbigailBalintSources.bib
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Intro {.sidebar}

Preparing the dashboard based on the instructions given at @magallanes_reyes_data_2022, and @sievert_flexdashboard_2022.

You can find the code for this dashboard here: https://github.com/abbybalint/DACSS690V_AbigailBalint_Final


### References
<div id="refs"></div>
“The Global AI, ML, Data Science Salary Index for 2024.” AI-Jobs, 2024, ai-jobs.net/salaries/2024/"

## Column {data-width="450"}

### Barplot - Work Location of Job Listings from Database

```{r}
readRDS("deliverable1.rds")
```

### Histogram - Number of Jobs Available in Database by Listed Salary

```{r}
readRDS("deliverable2.rds")
```

## Column {data-width="550"}

### Cat-Cat Bivariate Plot - Percentage of Jobs 2020-2024 that are Remote, Hybrid, vs In-Person

```{r}
readRDS("deliverable3.rds")
```


### Map - Map of the World Plotting Calculated Average Salary for Data Science Jobs by Country

```{r}
readRDS("deliverable4.rds")
```


